Hypertension and microbiome

### 2019-01-02 rrbiome.Rmd
Bug

```{r prepare maaslin}
prepare.maaslin <- function (pseq,
                             tsvfile = "merged_phfinrisk_genus.tsv",
                             conffile = "maaslin_config.config",
                             includedvars = c("BL_AGE", "BMI", "SEX")) {
    pheno <- t(microbiome::meta(phyloseq::sample_data(pseq)))
    sample.ids <- colnames(pheno)
    phfg.pseq.rel <- microbiome::transform(pseq, "compositional")
    abud.rel <- abundances(phfg.pseq.rel)
    rownames(abud.rel) <- sapply(rownames(abud.rel), function (genus) gsub("(.*) \\(+(.+)\\)", '\\1.\\2', genus))
    write.table(t(rbind(sample.ids, pheno, abud.rel)), file = tsvfile, sep='\t', quote=TRUE, row.names=TRUE, col.names=NA)
    data <- file(conffile , open='wt')
    pcl.contents <- c("Matrix: Metadata",
                      paste(c("Read_PCL_Rows: ", paste(includedvars, collapse=",")), collapse = ""),
                      "",
                      "Matrix: Adundance",
                      "Read_PCL_Rows: Archaea.Archaea-")
    writeLines(pcl.contents, con=data)
    close(data)
}

@@

```{r lactobacillus}

taxa <- subset_taxa(pseq.species, Genus=="Lactobacillus") %>% taxa()

>>>>

```{r prepare maaslin}
prepare.maaslin <- function (pseq,
                             tsvfile = "merged_phfinrisk_genus.tsv",
                             conffile = "maaslin_config.config",
                             includedvars = c("BL_AGE", "BMI", "SEX")) {
    pheno <- t(microbiome::meta(phyloseq::sample_data(pseq)))
    sample.ids <- colnames(pheno)
    phfg.pseq.rel <- microbiome::transform(pseq, "compositional")
    abud.rel <- abundances(phfg.pseq.rel)
    rownames(abud.rel) <- sapply(rownames(abud.rel), function (genus) gsub("(.*) \\(+(.+)\\)", '\\1.\\2', genus))
    write.table(t(rbind(sample.ids, pheno, abud.rel)), file = tsvfile, sep='\t', quote=FALSE, row.names=FALSE, col.names=TRUE)
    data <- file(conffile , open='wt')
    pcl.contents <- c("Matrix: Metadata",
                      paste(c("Read_PCL_Rows: ", paste(includedvars, collapse=",")), collapse = ""),
                      "",
                      "Matrix: Adundance",
                      "Read_PCL_Rows: Archaea.Archaea-")
    writeLines(pcl.contents, con=data)
    close(data)
}

@@

```{r lactobacillus, eval = FALSE}
pseq.lacto  <- subset_taxa(pseq.species, Genus=="Lactobacillus")
pseq.lacto.comp  <- microbiome::transform(pseq.lacto, "compositional")
abud.rel.lacto <- abundances(pseq.lacto.comp)

abud.rel.lacto %>%
    gather(Key, Value) %>%
    group_by(Subject, Type) %>%
     summarise_each(funs(mean= mean(., na.rm=TRUE)))
